%\section*{Collaborators}
%List all your collaborators.

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{color}
\usepackage{lipsum} % for filler text
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{enumitem}

\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\fancyhead{} % clear all header fields
\renewcommand{\headrulewidth}{0pt} % no line in header area
\fancyfoot{} % clear all footer fields
\fancyfoot[LE,RO]{\thepage}           % page number in "outer" position of footer line
\fancyfoot[RE,LO]{Aashish Dhakal} %your name in footer line

\begin{document}
%\lipsum[1-20]
\title{CS 572(Assignment 1)} %replace X with the appropriate number
\author{Aashish Dhakal\\ %replace with your name
aashish@iastate.edu\\%replace with username
 }      %if necessary, replace with your course title
\date{}


\maketitle
\section*{}

\textbf{Problem 2.3}
\begin{enumerate}[label=(\alph*)]
  \item False. The vacuum cleaning agent doesn't observe the state adjacent to it but is perfectly rational.
  \item True. If we touch fire than our reflex will be to pull our hand away from it.
  \item True. If all the actions and inactions produces the same result.
  \item False. Agent function has percept history as input while for Agent Program the percept history is current precept.
  \item False. A program when run for a longer period of time will eventually be out of memory, so there is no such gurantee that every agent function is
  implementable by some program/machine combination.
  \item True. If all the actions and inactions produces the same result.
  \item True. If both of the environments will be similar in any kind of way.
  \item False. If the agent doesn't have any way to perceive the environment and couldn't achieve it's goal then it wouldn't be rational.
  \item False. One of the player with better luck will win it.
\end{enumerate}

\textbf{Problem 2.6}
\begin{enumerate}[label=(\alph*)]
  \item Yes, there can be more than one agent program that implements a given agent function. For example,
  \item Yes, there are agent functions that cannot be implemented by any agent program. For eg: if there was an agent function to count the square root of a
  negative number.
  \item Yes. When given a fixed machine architecture the agent program will implement exactly one agent function, because if we want to implement multiple
  agent function we are require to select multiple actions i.e. multiple percepts. 
  \item There are $2^n$ possible agent programs.
  \item No, speeding up the machine wont change the agent function because the environment is still a static one but in some way it could make the machine
  better.
\end{enumerate}
\end{document}
}
